Deep Reinforcement Learning for Conservation Decisions

### 2021-02-04 manuscript/manuscript.Rmd
More bits to open issues

In the context of conservation, we anticipate that there will be a host of challenges. Interpretability is likely to be the biggest barrier to adoption. Although there have been some attempts to increase the transparency of RL agents that use neural network as function approximators [cite], it is still very difficult to explain the behavior of an RL-trained agent. Another challenge is that DRL algorithms are very sample inefficient, and to overcome sample inefficiency for conservation decision-making problems that are often data poor, relying on simulations to train agents will be necessary. While there are positives to using simulated data, any assumptions or biases that are included in the model will affect agent behavior.

A problem that is central to AI safety is selecting the right objective. There have been many examples in which explicit reward design goes horribly wrong [cite]. ...

>>>>

In the context of conservation, we anticipate that there will be a host of specific challenges to using DRL methods. Interpretability is likely to be the biggest barrier to adoption. Although there have been some attempts to increase the transparency of RL agents that use neural network as function approximators [cite], it is still very difficult to explain the behavior of RL-trained agents. Another challenge is that DRL algorithms are very sample inefficient, and to overcome sample inefficiency for conservation decision-making problems that are often data poor, relying on simulations to train agents will be necessary. While there are positives to using simulated data, any assumptions or biases that are included in the model will affect agent behavior.

A problem that is central to optimization in decision-making is using the right objective. There have been many examples in which explicit reward design goes horribly wrong [cite]. And for ecological systems, that are often very complex and impossible to fully observe, it seems that bad reward design is quite likely. One recently proposed framework to avoiding bad reward design is called AI alignment, wherein the agent observes humans, infers the preferences of humans and then acts as to satisfy human preferences. Yet, in the context of training an agent to say conserve a species, there are questions that could easily arise, foremost will the agent infer that humans don't care about a certain species so acts in a way that leads to that species' extinction? There is a definite need for exploration of the ethics of using DRL for conservation.

Specific to DRL, there
